### 2023-10-17 2.State/main.tex
Changed state orga
added new chapters
Tons of change, added GRU section
New figures + debut main

\input{2.State/1.memristors.tex}
\input{2.State/2.crossbar.tex}
\input{2.State/3.model.tex}
\input{2.State/4.lstm.tex}

>>>>

This chapter will go over the several subject that need to be known in order to understand the thesis.

Math is the best way to universally describe all scientific models. For this reason, this chapter, and the thesis as whole, will contains equations.

It seems only logical to define all the tools that are going to be used in the thesis.

\begin{itemize}
\item Vectors are displayed as $\overrightarrow{v}$ and are considered to be vertical matrixes when used in an equation.
\item $\overrightarrow{1}$ represent a vector that only contains ones of variable size.
\item $\odot$ is used for the Hadamart product, that is the point wise multiplication of each element of the matrixes
\item $\cdot$ is used in two cases :
\begin{itemize}
\item When used with a number, it is the product of those numbers.
\item When used with matrixes, it is the matrix product
\end{itemize}
\end{itemize}

\input{2.State/ai.tex}
\input{2.State/nn.tex}
\input{2.State/rnn.tex}
\input{2.State/lstm.tex}
\input{2.State/gru.tex}
\input{2.State/memristors.tex}
\input{2.State/crossbar.tex}
\input{2.State/model.tex}
